Active Learning from Blackbox to Timed Connectors

### 2016-01-19 paper/paper.tex
.

\begin{example}[FIFO1]
  \label{example:pmmfifo}
  The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \small
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          \rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
          \rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
          \rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
          \rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
          \{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
          \rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \small
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
          q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
          q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

@@

\begin{example}[n-Timer]
  The PMM of an n-Timer with a source-end A and a sink-end B can be defined as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_{i,d}|0\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \small
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          \{B\mapsto d\} & s=q_{n,d}\land i=\{A\mapsto \_,B\mapsto \rread\}\\
          \rblock & s=q_{n,d}\land \\
          & (i=T\lor i=\{A\mapsto \_,B\mapsto \rnoread\}) \\
          \rblock & s=q_{j,d}\land 0 \leq j < n\land \\
          & (i=\{A\mapsto \_,B\mapsto \rread\}\lor \\
          & i=\{A\mapsto d,B\mapsto \_\})\\
          \rempty & otherwise\\
        \end{array}
        \right.
      \end{displaymath} 
    \item[-] transition function
      \begin{displaymath}
        \small
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_{0,d} & s=q_0 \land i=\{A\mapsto d,B\mapsto \_\} \\
          q_{j+1,d} & s=q_{j,d}\land i=T\land0 \leq j < n\\
          q_0 & s=q_{n,d}\land i=\{A\mapsto \bot,B\mapsto \rread\} \\
          q_{0,d'} & s=q_{n,d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
          q_0 & s=q_{n,d} \land i=T \\
          s & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

@@

  \begin{itemize}
  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}.S(\Sigma)$
    \item[-] $\mathcal{PM}'.I=\mathcal{PM}.I\backslash\{\IN\}$
    \item[-] $\mathcal{PM}'.O=\mathcal{PM}.O\backslash\{\OUT\}$
    \item[-] $\mathcal{PM}'.s_0=\mathcal{PM}.s_0$
    \item[-] $\forall\Sigma, i\in
      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
      \begin{displaymath}
        \small
        \left\{
        \begin{array}[h]{lr}
          \rempty & i=T \\
          \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where the condition (*) is defined as
      \[
      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})(\OUT)=d
      \]
    \item[-] $\forall\Sigma, i\in
      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
      \begin{displaymath}
        \small
        \mathcal{PM}.\lambda(\Sigma)(s,i)=
        \left\{
        \begin{array}[ht]{lr}
          \mathcal{PM}.\lambda(\Sigma,T) & i=T \\
          \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN:d\}) & (*)\\
          s & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{definition}

@@

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we use L* algorithm to extract Reo coordinators from blackbox
implementations in 3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
Here the input symbols and output symbols of the blackbox are supposed to be provided as $\mathcal{I}$
and $\mathcal{O}$.

\subsection{Observation Table}
Results of membership queries come out as $mq(s)=o$, where $s\in\mathcal{I}+$.
Now the question is, \emph{how to find the connection betweensuch query results and Mealy machines?}

Generally, Mealy machines are composed of \emph{states} and \emph{transitions}.
Provided with a Mealy machine $m$, any input sequence in $m.I^+$ leads to a unique state. 
Such a sequence is called an \emph{access sequence} of this state.
Particularly, we use $\varepsilon$, the \emph{empty sequnce}, to denote the initial state.
Similarly, if a blackbox model has the same bahavior with a Mealy machine, we can use access
sequences to label its states and, in the same way, input actions to label its transitions.
For example, we consider a Mealy machine which is staying in some state labelled by $s$. With an
action $a$ provided, the Mealy machine will jump to a new state labelled by $s'=sa$ and generate an
output $mq(sa)$.

Different access sequences may lead to similar states. Here we use \emph{suffixes} set $D$ to
distinguish states where $D\subseteq \mathcal{I}^+$ is initialized as $\{d=\{i\}|i\in\mathcal{I}\}$. 
\begin{definition}[Equivalence under Suffixes]
  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
  the corresponding states of $s_1$ and $s_2$ are equivalent under $D$ (denoted as $s_1\sim_D s_2$)
  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
\end{definition}

Since all this \emph{inputs} and \emph{outputs} can be observed outside the
model, we can use the same notations to describe a black box as a hypothetical Mealy machine.
Following this idea, \emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87},
shows a tabular form of such hypothetical models. In observation tables, rows represent states with
label of their access sequences and columns are labelled with suffixes. Successors of a state $s$ is,
intuitively, denoted as extended access sequences $sa$ where $a$ is a single input action. 
A cell with column-label $d$ and row-label $s$ should contain the value $mq(sd)$. Algorithm
\ref{alg:buildtable} shows how to build such an observation table.

@@

Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$ and the alphabet
is $\{a\}$. We briefly denote $\{A:a,B:\rnoread\}$ and other input/output actions in form of
$a,\rnoread$.

Firstly, $obs$ is initialized as empty and the empty sequence $\varepsilon$ is pushed in $unclosed$.
Then we will explore all the access sequences in $unclosed$ and calculate its successors. Here the
$unclosed$ set consists of access sequences that has no equivalent fellow with less length. 
For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
iteration. The five successors of $\varepsilon$ is presented as the bottom part of the table, where
four are equivalent with $\varepsilon$ but $a,\rnoread$ is not. Therefore, we take $a,\rnoread$ as a
brand-new state and all of its successors need further exploration (see in the hypothesis Mealy
machine presented in the following figure).

@@

\begin{figure}[ht]
  \begin{center}
    \begin{displaymath}
      \small
      \begin{array}{l||ccccc||c}
        \hline
        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
        \hline\hline
        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        \hline
        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        \hline
        a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
        \hline
      \end{array}
    \end{displaymath}
  \end{center}
  \caption{A Closed Observation Table}
  \label{fig:hypo2}
\end{figure}

\subsection{Counter-Examples' Analysis} 
Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not equal to the 2-Timer
channel. It's easy to find a counter-example $s=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.

Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
a sequence $s$, we use $acc(s)$ to denote the access sequence of $obs\xrightarrow{s}$ and $hq(s)$ to
denote the corresponding output.

\begin{definition}[Counter-Example]
  We use $hq$ to denote execution result of the hypothetical Mealy machine, sequence $s$ is called a
  counter-example iff $mq(s)\neq hq(s)$.
\end{definition}

@@

Considering a counter example $s$, we have
\[
\mbox{MaxSuffix}(s)=\max_d\{s=s'd, mq(acc(s')d)\neq mq(s)\}
\]
Since $mq(acc(s))=hq(s)\neq mq(s)$ and $mq(s) = mq(s)$, the existance of such $d$ is easy to prove.
After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
counter-example.

@@

Our future works would mainly focus on better support of dense time. To describe dense
time behavior, the Mealy machine model needs a lot of changes instead of a simple T action. Besides,
we will also try to improve our algorithm to handle non-deterministic behaviors. This is not a brand
new topic \cite{DBLP:journals/eceasst/VolpatoT15}, but we believe that there is still room for
improvement.  
\bibliographystyle{abbrv}
\bibliography{bib}

>>>>

\begin{example}[FIFO1]
  \label{example:pmmfifo}
  The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{small}
        \begin{displaymath}
          \delta(\Sigma)(s,i)=\left\{
          \begin{array}[ht]{ll}
            \rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
            \rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
            \rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
            \rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
            \{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
            \rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
          \end{array}
          \right.
        \end{displaymath}
      \end{small}
    \item[-] transition function
      \begin{small}
        \begin{displaymath}
          \lambda(\Sigma)(s,i)=\left\{
          \begin{array}[ht]{ll}
            q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
            q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
            q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
            q_0 & otherwise \\
          \end{array}
          \right.
        \end{displaymath}
      \end{small}
  \end{itemize}
\end{example}

@@

\begin{example}[n-Timer]
  The PMM of an n-Timer with a source-end A and a sink-end B can be defined as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_{i,d}|0\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{small}
        \begin{displaymath}
          \delta(\Sigma)(s,i)=\left\{
          \begin{array}[ht]{ll}
            \{B\mapsto d\} & s=q_{n,d}\land i=\{A\mapsto \_,B\mapsto \rread\}\\
            \rblock & s=q_{n,d}\land \\
            & (i=T\lor i=\{A\mapsto \_,B\mapsto \rnoread\}) \\
            \rblock & s=q_{j,d}\land 0 \leq j < n\land \\
            & (i=\{A\mapsto \_,B\mapsto \rread\}\lor \\
            & i=\{A\mapsto d,B\mapsto \_\})\\
            \rempty & otherwise\\
          \end{array}
          \right.
        \end{displaymath} 
      \end{small}
    \item[-] transition function
      \begin{small}
        \begin{displaymath}
          \lambda(\Sigma)(s,i)=\left\{
          \begin{array}[ht]{ll}
            q_{0,d} & s=q_0 \land i=\{A\mapsto d,B\mapsto \_\} \\
            q_{j+1,d} & s=q_{j,d}\land i=T\land0 \leq j < n\\
            q_0 & s=q_{n,d}\land i=\{A\mapsto \bot,B\mapsto \rread\} \\
            q_{0,d'} & s=q_{n,d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
            q_0 & s=q_{n,d} \land i=T \\
            s & otherwise \\
          \end{array}
          \right.
        \end{displaymath}
      \end{small}
  \end{itemize}
\end{example}

@@

  \begin{itemize}
  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}.S(\Sigma)$
    \item[-] $\mathcal{PM}'.I=\mathcal{PM}.I\backslash\{\IN\}$
    \item[-] $\mathcal{PM}'.O=\mathcal{PM}.O\backslash\{\OUT\}$
    \item[-] $\mathcal{PM}'.s_0=\mathcal{PM}.s_0$
    \item[-] $\forall\Sigma, i\in
      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
      \begin{small}
        \begin{displaymath}
          \left\{
          \begin{array}[h]{lr}
            \rempty & i=T \\
            \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
            \rblock & otherwise \\
          \end{array}
          \right.
        \end{displaymath}
      \end{small}
      where the condition (*) is defined as
      \[
      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})(\OUT)=d
      \]
    \item[-] $\forall\Sigma, i\in
      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
      \begin{small}
        \begin{displaymath}
          \mathcal{PM}.\lambda(\Sigma)(s,i)=
          \left\{
          \begin{array}[ht]{lr}
            \mathcal{PM}.\lambda(\Sigma,T) & i=T \\
            \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN:d\}) & (*)\\
            s & otherwise \\
          \end{array}
          \right.
        \end{displaymath}
      \end{small}
  \end{itemize}
\end{definition}

@@

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we use L* algorithm to extract Reo coordinators from blackbox
implementations in 3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
here the input and output symbols of the blackbox are provided as $\mathcal{I}$ and $\mathcal{O}$,
and the blackbox implementation is supposed to be equivalent to a Mealy machine where all states are
reachable.

\subsection{Observation Table}
\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, is used to construct
a hypothetical Mealy machine from results membership queries.

Generally, a Mealy machines is determined by its \emph{states} and \emph{transitions}.
As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
after execution of $s$. Similarly, for all $a\in\mathcal{I}$, $sa$ indicates the successor
state of $s$ after execution of $a$.
However, under such notations, there are \emph{infinite} number of states where most are
reduplicate.

States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
\mathcal{I}^*$, the corresponding of $s_1$ and $s_2$ are exactly the same iff $\forall d\in
\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
\begin{definition}[$D$-Equivalence]
  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
  the corresponding states of $s_1$ and $s_2$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
\end{definition}
\begin{definition}[Access Sequence]
  Given an input sequence $s$, we define the access sequence of $s$ as
  \[
  acc(s,D)=\min\{s'\in\mathcal{I}^*|s'\sim_D s\}
  \]
\end{definition}

Formally, an observation table is defined as a tuple $(S,D)$ where $S\subset\mathcal{I}^*$ indicates
the access sequences of states and $D\subset\mathcal{I}^*$ indicates the suffixes. Its
tabular form can be found in Figure \ref{fig:hypo}. In such tables, columns are labelled with
$d\in D$, and rows are labelled with input sequences. Rows are divided into two parts. The upper
part, labelled with $s\in S$, shows the states in current hypothesis (in form of access sequences).
The lower part, labelled with $sa$ (where $s\in S,a\in\mathcal{I}$) indicates all the transitions
from $S$. A cell with row label $s$ and column label $d$ is filled with $mq(sd)$.

An observation table $(S,D)$ is \emph{closed} if 
\[
\forall s\in S,a\in\mathcal{I}.\exists s'\in S. sa\sim_D s'
\]

Algorithm \ref{alg:buildtable} shows how to build an closed observation table.

@@

Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$, and the alphabet
is $\{a\}$. We briefly denote $\{A:a,B:\rnoread\}$ and other input/output actions in form of
$a,\rnoread$.

Firstly, $obs$ is initialized as empty and the empty sequence $\varepsilon$ is pushed in $unclosed$.
Then we will explore all the access sequences in $unclosed$ and calculate its successors. Here the
$unclosed$ set consists of access sequences that has no equivalent fellow in $S$. 
For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
iteration. The five successors of $\varepsilon$ is presented as the bottom part of the table, where
four are equivalent with $\varepsilon$ but $a,\rnoread$ is not. Therefore, we take $a,\rnoread$ as a
brand-new state and all of its successors need further exploration (see in the hypothesis Mealy
machine presented in the following figure).

@@

\begin{figure}[ht]
  \begin{center}
    \begin{small}
      \begin{displaymath}
        \begin{array}{l||ccccc||c}
          \hline
          & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
          \hline\hline
          \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
          \hline
          a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
          \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
          a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
          T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
          \hline
          a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
          \hline
        \end{array}
      \end{displaymath}
    \end{small}
  \end{center}
  \caption{A Closed Observation Table}
  \label{fig:hypo2}
\end{figure}

\subsection{Counter-Examples' Analysis} 
Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not the 2-Timer
channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.

Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
a sequence $s$, we use $hq(obs,s)$ to denote the execution result of $obs$ under the input sequence
$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $a$ is the last element of $s$ and $s=s'a$.

\begin{definition}[Counter-Example]
  sequence $s$ is called a counter-example of $obs$ iff $mq(s)\neq hq(obs,s)$.
\end{definition}

@@

Considering a counter example $s$, we define the function MaxSuffix($s,obs$) as
\[
\max\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
\]
After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
counter-example.

@@

Our future works would mainly focus on better support of dense time. To describe dense
time behavior, the Mealy machine model needs a lot of changes instead of a simple T action. Besides,
we will also try to improve our algorithm to handle non-deterministic behaviors. This is not a brand
new topic \cite{DBLP:journals/eceasst/VolpatoT15}, but we believe that there is still room for
improvement.

\bibliographystyle{IEEEtran}
% \bibliography{IEEEabrv, bib}
\bibliography{bib}
